Temporary Landing Page for Longitudinal Project

### 2023-04-23 index.qmd
landing page update

---
title: "swhawes.github.io"
---

This is a Quarto website.

To learn more about Quarto websites visit <https://quarto.org/docs/websites>.

>>>>

---
#title: "Temporary Landing Page for Longitudinal Project"
#format:
#  html:
#    css: styles.css
#    theme: cosmo
#    fontsize: 1.1em
    #linestretch: 1.7
---

<div class="text-3xl text-center">
This is the temporary landing page for the Longitudinal Analysis Project. <br> The site is currently under construction and used for testing purposes only. <br> Contents may be inaccurate.
</div>

<br>

::: {.grid}

::: {.g-col-2}
:::

::: {.g-col-8}
![](./figures/lights.png)
:::

::: {.g-col-2}
:::

:::

</div>
